Complex Quasiperiodic Variables from Four Years of TESS

### 2023-06-12 paper/ms.tex
update ms

%%%%%%%%
% CPVS %
%%%%%%%%
\newcommand{\ncpvsfound}{{48}}
\newcommand{\nmaybes}{{19}}

@@

\title{Bright and Nearby Complex Periodic Variables from Four Years of TESS}

@@

\received{---}
\revised{---}
\accepted{---}
\shorttitle{Cycle 1-4 CPVs}

@@

\begin{abstract}
  Complex periodic variables (CPVs) are pre-main-sequence M-dwarfs
  with periodic optical modulation that includes both sharp and broad
  troughs.
  The troughs are usually superposed on smooth, spot-like modulation.
  Based on a lack of observed infrared excesses, these objects do not
  have primordial gas-rich disks, or even particularly massive debris disks.
  Nonetheless, the most plausible explanations for their optical
  variability invoke long-lived material that orbits at the corotation
  radii, for instance transiting dust clumps or stellar prominences.
  Here, we report new CPVs discovered in the 120-second cadence TESS data
  collected between July~2018 and Sep~2022 (Sectors 1-55).
  Our search used two methods, the first based on counting dips in
  phase-folded light curves, and the second based on counting peaks in
  the Fourier domain.
  From our analysis of \nstarssearched\ M-dwarfs with $T$$<$16 and
  $d$$<$150\,pc, we find \ncpvsfound\ gold-standard CPVs.
  Most of these discoveries are new, and they include the brightest
  ($T$$\approx$10) and closest ($d$$\approx$20\,pc) examples of this
  class of variable star known.
  A few objects are ``outliers among outliers''; for
  instance LP 12-502 shows up to eight local minima per cycle, exhibited
  sudden shape ``switches'' over less than one cycle, yet maintained
  a near-constant cycle duration over more than one thousand cycles.
  The general cause of the optical variability for these objects remains
  enigmatic.  However our sample is a step toward the spectroscopic and
  demographic studies that may ultimately resolve the mystery of what
  physically explains these objects.
  Connections to the broader context of star, disk, and
  exoplanet evolution are emphasized.
\end{abstract}

@@

All pre-main-sequence stars vary in optical brightness, and the origin
of such variability is, in most cases, understood.  Well-explored
sources of optical variability include inhomogeneities on stellar
surfaces such as starspots and faculae
\citep[e.g.][]{2021isma.book.....B}, occultations by gas-rich
circumstellar disks \citep[e.g.][]{2017MNRAS.470..202B}, and, in
geometrically favorable circumstances, eclipses by stars and planets.

Data from K2 and TESS have yielded a new class of variable star whose
root cause is not yet qualitatively understood: complex periodic
variables (CPVs).  These objects are identified phenomenologically
using their optical light curves, which show periodic sharp and
sometimes broad troughs, often superposed on smooth spot-like
modulation.  Some of the objects show up to eight local minima (dips)
per cycle; sharp peaks are also common.  Most of these variable stars
turn out to be pre-main-sequence M-dwarfs without near-infrared
excesses, with ages of $\approx$5-150 million years (Myr), and
rotation periods of at most two days; they are observed to be
$\approx$1\% of M-dwarfs younger than 100 Myr
\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G}.
The dips can be chromatic, with a reddening law plausibly consistent
with dust
\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
And finally, while the dip shapes can ``jump'' between different
depths and durations over less than one cycle, they more often evolve
gradually, over tens to hundreds of cycles
\citep[e.g.][]{2017AJ....153..152S,2020AJ....160...86B,2023ApJ...945..114P}.

The issue of what exactly causes the variability that defines the CPVs
has yet to be resolved.  There are a few competing explanations.  All
young M-dwarfs are spotted, which produces flux variations over
characteristic timescales of the rotation period, $P_{\rm rot}$, and
its half-harmonic, $0.5\,P_{\rm rot}$.  The observed dips occur over
durations as short as $0.05\,P_{\rm rot}$; a ``starspot-only''
scenario is therefore highly unlikely for any of the objects with
sufficiently sharp dips
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The more likely
scenarios instead invoke sharp geometries with material extrinsic to
the stellar surface \citep[see
Refs.~][]{2017AJ....153..152S,2022AJ....163..144G}.  In the ``clump''
scenario, opaque dust clumps orbiting near the Keplerian corotation
radius eclipse the star
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  In the
``prominence'' scenario, long-lived condensations of plasma are
trapped along the star’s magnetic field lines, also near corotation
\citep{2022MNRAS.514.5465W}.  And in a ``screen'' scenario, the inner
wall of a quiescent circumstellar disk blocks a portion of the stellar
surface to produce sudden dips whenever spots come into view
\citep{2019ApJ...876..127Z}.  In our view, the arguments seem best
established for the dust clump and prominence hypotheses
\citep{2023MNRAS.518.4734S,2022MNRAS.514.5465W}.  However, unambiguous
evidence has yet to be presented to demonstrate which, if any, of
these scenarios is correct.

It has not yet been possible to rule between the candidate mechanisms
CPVs have historically been both hard to discover and hard
to characterize.   Discoverability has been linked to rarity: 
CPVs comprise about 1\% of the youngest 1\% of M-dwarfs
\citep{2018AJ....155..196R}.  Out of the millions of stars monitored
by K2 and TESS, about 50 CPVs have been reported to date
\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}.
The known CPVs are correspondingly faint; the initial K2 discoveries
\citep{2017AJ....153..152S} were M2-M6 dwarfs at distances
$\gtrsim$100\,pc, yielding optical brightnesses of $V$$\approx$15.5 to
$V$$>$20.  This renders time-series optical spectroscopy at high
resolution technically impossible, despite its potential utility in
ruling between the models.

One way to help rule between the mechanisms is to therefore find
bright and nearby CPVs, since these objects will be the most amenable
to detailed photometric and spectroscopic analyses.  To do this, in
this work, we use 120-second cadence data acquired by the Transiting
Exoplanet Survey Satellite between July~2018 and Sep~2022 (Sectors
1-55; Cycles 1-4).  We present our search methods in
Section~\ref{sec:methods}; and the properties of the resulting CPV
catalog in Section~\ref{sec:results}.  Open questions are discussed in
Section~\ref{sec:discussion}, and we conclude in
Section~\ref{sec:conclusion}.

@@

%We will first describe our stars of interest
%(Section~\ref{subsec:selectionfn}), and then describe our methods for
%identifying which of those stars appear as CPVs
%(Section~\ref{subsec:discoverymethods}).

@@

		\subfloat{
			\includegraphics[width=0.8\textwidth]{models.pdf}
		}
		%\subfloat{
		%	\includegraphics[width=0.8\textwidth]{flux_vs_time_xmin0000_xmax0010.pdf}
		%}
	\end{center}
	\caption{
		{\bf Complex periodic variables (CPVs)}:
		{\it Top:} Phase-folded TESS light curves of three CPVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  In order left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Plausible cartoon models for the phenomenon.
		%{\it Bottom:} Flux {\it vs.}~time showing 10 cycles for each
		%object.  Raw 2-minute data are the gray background; the black line
		%is drawn between points binned to 1/100$^{\rm th}$ of a cycle.
	}
	\label{fig:f1}
%	\vspace{-0.5cm}
\end{figure*}

\subsection{CPV discovery}
\label{subsec:discoverymethods}

Previous methods that have yielded CPV discoveries include visually
examining stars known to be in young clusters
\citep{2017AJ....153..152S}, and automatically flagging rapid rotators
with a large number of strong Fourier harmonics
\citep{2019ApJ...876..127Z}.  The latter approach is followed by
visual vetting, since most rapid rotators with many Fourier harmonics
are false positives such as eclipsing binaries or multiple stars
blended into a single photometric aperture.  In this work, we adopted
the Fourier approach,
and also implemented a new search approach based on counting the
number of sharp local minima in phase-folded light curves.  We then
applied these two search techniques independently.

@@

The dip counting technique aims to count sharp local minima in
phase-folded light curves.  CPVs will preferably have at least three
such minima in order to be distinct from false positives such as
synchronized and spotted binaries (``RS CVn'' stars).

@@

To correctly identify local minima near the edges of the phased light
curve, which usually would cover phases $\phi \in [ 0,1 ]$, we in fact
performed the entire procedure over a phase-folded light curve
spanning $\phi \in [-1,2 ]$, by duplicating and concatenating
the ordinary phase-folded light curve.
The free parameters we adopted throughout this analysis procedure, for
instance the maximum number of spline knots per cycle, and how large
and wide of a local minimum to consider a ``true dip'', were chosen
during a testing period based on their ability to correctly re-identify 
a large fraction ($>$90\%) of known CPVs, while also being able to
consistently reject common false positives such as rapidly rotating
spot-induced variability and typical eclipsing binaries.

@@

\subsection{Manual vetting}

We visually assessed whether the objects found using the Fourier
(Section~\ref{subsec:fourier}) and dip-counting
(Section~\ref{subsec:counting}) techniques were consistent with 
expectations for CPVs by assembling 
the data shown in Appendix~\ref{app:vetting}.
The false-positive rates from our dip-counting approach, as-implemented,
%TODO: left off here

While
the highest S/N cases were generally found by both the Fourier and dip-counting
techniques, we
generally found that

@@

\begin{figure*}[!tp]
	\begin{center}
    \centering
    \includegraphics[width=\textwidth]{lc_mosaic_dlt150_good_all.pdf}
		\caption{
			{\bf CPVs from a search of the TESS 2-minute data at
      $d$$<$150\,pc, acquired between July~2018 and Sep~2022.}
      Phased TESS light curves over 1 month are shown for 40 CPVs;
      they include the brightest and closest examples of CPVs known
      ($V$=14; $J$=9.5; $d$=25\,pc).  Gray are raw 2-minute data;
      black bins to 300 points per cycle.  Periods in hours are listed
      in the lower right corners of each panel.
      The TIC identification numbers and sectors are listed in
      Table~\ref{tab:thetable}.
		}
		\label{fig:revolution}
%		\vspace{-0.8cm}
	\end{center}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
			\centering
			\includegraphics[width=0.9\textwidth]{lc_mosaic_dlt150_good_changers.pdf}
		\vspace{-0.2cm}
		\caption{
		{\bf Evolution of CPVs}: ``Before and
      after'' for six CPVs from Figure~\ref{fig:revolution}.  Panels
      in the top two rows are separated by two years
      ($\approx$$10^3$ cycles); each panel shows one month.
      Periods are listed in hours. 
      {\bf todo: make these for everything.}
%			\vspace{-0.8cm}
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

@@

%A number of auxiliary
%questions follow.  After correcting for line-of-sight inclination, are
%most young M-dwarfs CPVs?  What observational signatures distinguish
%the proposed models (Figure~\ref{fig:f1}, bottom row)?  What
%organizational regularities characterize the CPV as a class of
%variable star?  What sets the extremes of the CPV population, such as
%the longest rotation periods, hottest stellar temperatures, and oldest
%stellar ages?  And finally, what connections, if any, do CPVs have to
%topics such as stellar evolution, M-dwarf magnetic fields, debris
%disks, and close-in exoplanets?

@@

Figure~\ref{fig:vet} shows the type of plot used to visually assess
whether a source was likely to be a CPV, eclipsing binary, or simply a
rapidly rotating star.

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=\textwidth]{402980664_S0019_120sec_cpvvetter.pdf}
		\vspace{-0.45cm}
		\caption{
      Validation plots used to label CPVs (the complete figure
      set of \ncpvsfound\ images is available online).
      Panels are as follows.
      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
      data and black points are binned to 200 points per cycle.
      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
      circles displayed for scale.
      {\it d)}: Cleaned light curve, binned to 20-minute cadence.
      {\it e)}: Phase-folded light curve, binned to 100 points per
      cycle.  The gray line denotes the automated spline-fit to the
      wrapped phase-folded light curve, and small gray triangles
      denote automatically identified local minima; 
      one of the four sharp dips for this star was not identified!
      {\it f)}: Phase-folded light curve at twice the peak period.
      {\it g)}: Phase-folded light curve at half the peak period.
      {\it h)}: Phase-folded time-series within the ``background''
      aperture defined in the SPOC light curves.
      {\it i)}: Phase-folded flux-weighted centroid in the column
      direction.
      {\it j)}: Phase-folded flux-weighted centroid in the row
      direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      }
		\label{fig:vet}
	\end{center}
\end{figure*}

>>>>

%%%%%%%%
% CQVS %
%%%%%%%%
% dip-counting pipeline
\newcommand{\nuniqdipflagged}{{368}} % up-to-date; get_lgb_list_count.py
\newcommand{\ncpvsfound}{{48}}
\newcommand{\nmaybes}{{19}}

@@

\title{Complex Quasiperiodic Variables from Four Years of TESS}

@@

\received{---}
\revised{---}
\accepted{---}
\shorttitle{Cycle 1-4 CQVs}

@@

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are pre-main-sequence M-dwarfs
  with almost-periodic optical modulation that includes both sharp and broad
  troughs.  The troughs are usually superposed on smooth, spot-like
  modulation.  Based on a lack of observed infrared excesses, these
  objects do not have primordial gas-rich disks.  Nonetheless, the
  currently preferred explanations for their optical variability invoke
  long-lived material that orbits at the corotation radii, for
  instance transiting dust clumps or stellar prominences.  Here, we
  report new CQVs discovered in the 120-second cadence TESS data
  collected between July~2018 and Sep~2022 (Sectors 1-55).  Our search
  used two methods, the first based on counting dips in phase-folded
  light curves, and the second based on counting peaks in the Fourier
  domain.  From our analysis of \nstarssearched\ M-dwarfs with
  $T$$<$16 and $d$$<$150\,pc, we find \ncpvsfound\ gold-standard CQVs.
  Most of these discoveries are new, and they include the brightest
  ($T$$\approx$10) and closest ($d$$\approx$20\,pc) examples of this
  class of variable star known.  A few objects are ``outliers among
  outliers''; for instance LP 12-502 shows between four and eight
  local minima per cycle, distributed over a ``dip complex'' with
  fixed total duration over more than one thousand cycles, but that
  has a detailed shape that at times showed significant changes over only one
  cycle.  More generally, we find that exactly zero of the CQVs
  maintain an identical light curve morphology over timescales of more
  than a few hundred cycles.  While the physical explanation behind
  these objects remains enigmatic, our sample is a step toward the
  spectroscopic and demographic studies that may help clarify their
  origin.  Connections to star, disk, and
  exoplanet evolution are emphasized.
\end{abstract}

@@

All pre-main-sequence stars vary in optical brightness, and the origin
of such variability is, in most cases, understood.  Well-explored
sources of optical variability include inhomogeneities on stellar
surfaces such as starspots and faculae
\citep{2021isma.book.....B}, occultations by gas-rich
circumstellar disks \citep{2017MNRAS.470..202B}, and, in
geometrically favorable circumstances, eclipses by stars and planets.

Data from K2 and TESS have yielded a new class of variable star whose
root cause is not yet qualitatively understood: complex quasiperiodic
variables (CQVs).  These objects are identified phenomenologically
using their optical light curves, which show quasiperiodic troughs
that can be either sharp or broad, often superposed on smooth
spot-like modulation.  Some of the objects show up to eight local
minima (dips) per cycle; sharp peaks are also common.  Most of these
variable stars turn out to be pre-main-sequence M-dwarfs without
near-infrared excesses, with ages of $\approx$5-150 million years
(Myr), and rotation periods of at most two days; they are observed to
be $\approx$1\% of M-dwarfs younger than 100 Myr
\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G}.
The dips can be chromatic, with a reddening law plausibly consistent
with dust
\citep{2020AJ....160...86B,2022AJ....163..144G,2023MNRAS.518.2921K}.
And finally, while the dip shapes can ``jump'' between different
depths and durations over less than one cycle, they more often evolve
gradually, over tens to hundreds of cycles
\citep[e.g.][]{2017AJ....153..152S,2023ApJ...945..114P}.

The issue of what exactly causes the variability that defines the CQVs
has yet to be resolved.  There are a few competing explanations.  All
young M-dwarfs are spotted, which produces flux variations over
characteristic timescales of the rotation period, $P_{\rm rot}$, and
its half-harmonic, $0.5\,P_{\rm rot}$.  The observed dips occur over
durations as short as $0.05\,P_{\rm rot}$; a ``starspot-only''
scenario is therefore highly unlikely for any of the objects with
sufficiently sharp dips
\citep{2017AJ....153..152S,2021MNRAS.500.1366K}.   The more likely
scenarios instead invoke sharp geometries with material extrinsic to
the stellar surface \citep[see
Refs.~][]{2017AJ....153..152S,2022AJ....163..144G}.  In the ``clump''
scenario, opaque dust clumps orbiting near the Keplerian corotation
radius eclipse the star
\citep{2017AJ....153..152S,2023MNRAS.518.4734S}.  In the
``prominence'' scenario, long-lived condensations of plasma are
trapped along the star’s magnetic field lines, also near corotation
\citep{2022MNRAS.514.5465W}.  And in a ``screen'' scenario, the inner
wall of a quiescent circumstellar disk blocks a portion of the stellar
surface to produce sudden dips whenever spots come into view
\citep{2019ApJ...876..127Z}.  In our view, the arguments seem best
established for the dust clump and prominence hypotheses
\citep{2023MNRAS.518.4734S,2022MNRAS.514.5465W}.  However, unambiguous
evidence has yet to be presented to demonstrate which, if any, of
these scenarios is correct.

It has not yet been possible to rule between the candidate mechanisms
CQVs have historically been both hard to discover and hard
to characterize.   Discoverability has been linked to rarity: 
CQVs comprise about 1\% of the youngest 1\% of M-dwarfs
\citep{2018AJ....155..196R}.  Out of the millions of stars monitored
by K2 and TESS, about 50 CQVs have been reported to date
\citep{2017AJ....153..152S,2018AJ....155...63S,2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}.
The known CQVs are correspondingly faint; the initial K2 discoveries
\citep{2017AJ....153..152S} were M2-M6 dwarfs at distances
$\gtrsim$100\,pc, yielding optical brightnesses of $V$$\approx$15.5 to
$V$$>$20.  This renders time-series optical spectroscopy at high
resolution technically impossible, despite its potential utility in
ruling between the models.

One way to help rule between the mechanisms is to therefore find
bright and nearby CQVs, since these objects will be the most amenable
to detailed photometric and spectroscopic analyses.  To do this, in
this work, we use 120-second cadence data acquired by TESS between July~2018 and Sep~2022 (Sectors
1-55; Cycles 1-4).  We present our search methods in
Section~\ref{sec:methods}; and the properties of the resulting CQV
catalog in Section~\ref{sec:results}.  Open questions are discussed in
Section~\ref{sec:discussion}, and we conclude in
Section~\ref{sec:conclusion}.

A point on nomenclature.  CQVs have been called ``transient and
persistent flux dips'', ``scallop shells'', ``batwings'',
\citep{2017AJ....153..152S,2018AJ....155...63S} ``complex rotators'',
\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
CQVs are not ``dippers'', which are classical T Tauri stars with
infrared excesses whose optical variability is linked to obscuring
inner disk structures and accretion hot spots (CITE Cody2014,
ConnorRobinson2021).  At the risk of introducing yet another standard,\footnote{\url{https://xkcd.com/927/}}
we prefer to make the
technical distinction that the CQVs are, over timescales of more than
a few cycles, not exactly periodic.  Their shapes evolve, usually over
some decoherence timescale, similar to variability induced by surface
inhomogeneities such as starspots.  While the three-type
classification scheme proposed by \citet{2017AJ....153..152S} may
indeed provide some helpful visual distinctions among the CQV class,
it seems likely (we hope!) that they are all explained by a single
underlying phenomenon, and so we opt to refer to them by a single
empirically descriptive name.

@@

@@

		\vspace{-0.15cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{models.pdf}
		}
	\end{center}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  In order left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Plausible cartoon models for the phenomenon.
		The ``clump'' or ``prominence'' scenarios seem most plausible,
		given the stability of the phenomenon and the lack of observed infrared excesses.
	}
	\label{fig:f1}
\end{figure*}

\subsection{CQV discovery}
\label{subsec:discoverymethods}

Previous methods that have yielded CQV discoveries include visually
examining stars known to be in young clusters
\citep{2017AJ....153..152S}, and automatically flagging rapid rotators
with a large number of strong Fourier harmonics
\citep{2019ApJ...876..127Z}.  The latter approach is followed by
visual vetting, since most rapid rotators with many Fourier harmonics
are false positives such as eclipsing binaries or multiple stars
blended into a single photometric aperture.  In this work, we adopted
the Fourier approach, and also implemented a new search approach based
on counting the number of sharp local minima in phase-folded light
curves.  We then applied these two search techniques independently.

@@

The dip counting technique aims to count sharp local minima in
phase-folded light curves.  CQVs will preferably have at least three
such minima in order to be distinct from false positives such as
synchronized and spotted binaries (``RS CVn'' stars).

@@

To correctly identify local minima near the edges of the phased light
curve, which usually would cover phases $\phi \in [ 0,1 ]$, we in fact
performed the entire procedure over a phase-folded light curve
spanning $\phi \in [-1,2 ]$, by duplicating and concatenating the
ordinary phase-folded light curve.  The free parameters we adopted
throughout this analysis procedure, for instance the maximum number of
spline knots per cycle, and how large and wide of a local minimum to
consider a ``true dip'', were chosen during a testing period based on
their ability to correctly re-identify a large fraction ($>$90\%) of
known CQVs, while also being able to consistently reject common false
positives such as rapidly rotating spot-induced variability and
typical eclipsing binaries.

@@

\subsubsection{Manual vetting}

We visually assessed whether the objects found using the Fourier
(Section~\ref{subsec:fourier}) and dip-counting
(Section~\ref{subsec:counting}) techniques were consistent with
expectations for CQVs by assembling the data shown in
Appendix~\ref{app:vetting}.

Broadly speaking, the most common false positives for both the Fourier
and dip-counting techniques were eclipsing binaries, spot-induced
variability from rapid rotators, and blended combinations thereof.
Rarer false positives included disk-induced variability, for instance
induced by quasiperiodic dippers (CITE).  Typical false postive rates
from our dip-counting pipeline were 5:1, with 368 unique stars
flagged, and about 20\% being labelled either ``good'' or ``possible''
CQVs; for the Fourier pipeline, {\bf the rate was X:Y, with ZZZZ
unique stars flagged, and NN\% being labelled ``good'' or ``possible''
CQVs}.

\subsection{Stellar properties}

\paragraph{Ages}
%TODO

\paragraph{Effective temperatures, radii, and masses}
%TODO

@@

\subsection{CQV catalog}

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=\textwidth]{lc_mosaic_dlt150_good_all.pdf}
		\caption{
			{\bf CQVs from a search of the TESS 2-minute data at
      $d$$<$150\,pc, acquired between July~2018 and Sep~2022.}
      Phased TESS light curves over 1 month are shown for 40 CQVs;
      they include the brightest and closest examples of CQVs known
      ($V$=14; $J$=9.5; $d$=25\,pc).  Gray are raw 2-minute data;
      black bins to 300 points per cycle.  Periods in hours are listed
      in the lower right corners of each panel.
      {\bf todo:  add TIC IDs and sector numbers}.
      % TODO: sort by brightness maybe?
      % TODO: sort by period?
		}
		\label{fig:singlemosaic}
	\end{center}
\end{figure*}

Table~\ref{tab:thetable} lists the \ncpvsfound\ CQVs identified by
our search, and some of their important properties.
The mosaic in Figure~\ref{fig:singlemosaic} shows the 40 brightest
objects.

For the TESS sectors in which these objects were identified, they show
anywhere from one to eight local minima per cycle.
Some stars show relatively ordinary modulation during one continuous
portion of the phased light curve, and highly structured modulation in
the remainder of the cycle (e.g. TIC~206544316, TIC~224283342,
TIC~402980664).
Others show structured modulation over the entire span of a cycle
(e.g. TIC~2234692, TIC~401789285, TIC~425933644, TIC~142173958).
Others still show some mix between these two modes,
with one or more small dips, superposed over one or more large dips.
Frankly, staring at them for long enough,
it becomes possible to identify any one of them

\subsection{CQV evolution}

\paragraph{None of them are strictly periodic}

A periodic signal does not modulate.

\begin{figure*}[!t]
	\begin{center}
			\centering
			\includegraphics[width=0.9\textwidth]{lc_mosaic_dlt150_good_changers.pdf}
		\vspace{-0.2cm}
		\caption{
		{\bf Evolution of CQVs}: ``Before and
      after'' for six CQVs from Figure~\ref{fig:revolution}.  Panels
      in the top two rows are separated by two years
      ($\approx$$10^3$ cycles); each panel shows one month.
      Periods are listed in hours. 
      {\bf todo: make these for everything.}
%			\vspace{-0.8cm}
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

@@

{\it Each CQV a snowflake}
One intriguing aspect of staring at Figure~\ref{fig:singlemosaic}
is that, even after rescaling the amplitudes, no two CQVs
exhibit exactly identical light curve morphology.
There are of course similarities.

TIC 272248916 and TIC 442571495

%A number of auxiliary
%questions follow.  After correcting for line-of-sight inclination, are
%most young M-dwarfs CQVs?  What observational signatures distinguish
%the proposed models (Figure~\ref{fig:f1}, bottom row)?  What
%organizational regularities characterize the CQV as a class of
%variable star?  What sets the extremes of the CQV population, such as
%the longest rotation periods, hottest stellar temperatures, and oldest
%stellar ages?  And finally, what connections, if any, do CQVs have to
%topics such as stellar evolution, M-dwarf magnetic fields, debris
%disks, and close-in exoplanets?

@@

Figure~\ref{fig:vet} shows the type of plot used to visually assess
whether a source was likely to be a CQV, eclipsing binary, or simply a
rapidly rotating star.

\begin{figure*}[!t]
	\begin{center}
    \centering
    \includegraphics[width=\textwidth]{402980664_S0019_120sec_cpvvetter.pdf}
		\vspace{-0.45cm}
		\caption{
      Validation plots used to label CQVs (the complete figure
      set of \ncpvsfound\ images is available online).
      Panels are as follows.
      {\it a)}: Phase-folded light curve; gray points are raw 2-minute
      data and black points are binned to 200 points per cycle.
      {\it b)}: Phase-dispersion minimization (PDM) periodogram.
      {\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
      circles displayed for scale.
      {\it d)}: Cleaned light curve, binned to 20-minute cadence.
      {\it e)}: Phase-folded light curve, binned to 100 points per
      cycle.  The gray line denotes the automated spline-fit to the
      wrapped phase-folded light curve, and small gray triangles
      denote automatically identified local minima; 
      one of the four sharp dips for this star was not identified!
      {\it f)}: Phase-folded light curve at twice the peak period.
      {\it g)}: Phase-folded light curve at half the peak period.
      {\it h)}: Phase-folded time-series within the ``background''
      aperture defined in the SPOC light curves.
      {\it i)}: Phase-folded flux-weighted centroid in the column
      direction.
      {\it j)}: Phase-folded flux-weighted centroid in the row
      direction.
      {\it k)}: Gaia DR2 color--absolute magnitude diagram.     
      {\it l)}: Information from Gaia DR2, TIC8, and the automated
      dip-counting search pipeline.  ``Neighbors'', abbreviated
      ``nbhr'', are listed within apparent distances of 2 TESS pixels
      if $\Delta T$$<$2.5.
      }
		\label{fig:vet}
	\end{center}
\end{figure*}

\section{No additional power at 20~second cadence}

Going from K2 to TESS, an important discovery was that the CQV shapes
can significantly evolve, since the stars can vary over timescales of just a few minutes.
We observed a set of CQVs between 2020 and 2021 using the TESS 20-second
cadence mode (TESS DDT029).
{\bf todo: list the stars.  todo: examine the 2min vs 20sec periodograms, and summarize in a few
sentences whether any difference is there.}
